---
title: "Project results"
execute:
  warning: false
---

```{r}
#| include: false
lang <- "en"
source("../dados/resultados.R", encoding = "UTF-8")
r    <- resultados_dados()
```

An overview of what the SpectraPop Project has delivered so far: people trained, the spectral collection built and scientific output. The numbers of courses, people trained, supervised students and output are counted automatically from the Publications page. Updated in `r resultados_data_texto(lang)`.

## Training people

```{r}
#| echo: false
#| output: asis
resultados_cards(r, c("cursos", "treinados", "estudantes"), lang)
```

## Spectral collection and tools

```{r}
#| echo: false
#| output: asis
resultados_cards(r, c("espectros", "especies", "exsicatas", "apps"), lang)
```

Explore the spectral library on the [Spectral Library](spectral-library.qmd) page.

## Scientific output and outreach

```{r}
#| echo: false
#| output: asis
resultados_cards(r, c("artigos", "preprints", "livros", "resumos", "palestras", "eventos"), lang)
```

The full list, with links and DOIs, is on the [Publications](publications.qmd) page.
